\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2014-11-17 Proposal.tex
added Abstract draft

  Consider this a separate document, although it is submitted together
  with the rest. The abstract aims at another audience than the rest
  of the proposal. It is directed at the final decision maker or
  generalist, who typically is not an expert at all in your field, but
  more a manager kind of person. Thus, don't go into any technical
  description in the abstract, but use it to motivate the work and to
  highlight the importance of your project.

  (target size: 15-20 lines)

@@

  This, like the rest, addresses fellow experts from your field (but
  not from your particular topic of research). Here you should
  technically connect to the main concepts from that field and give an
  outline of your project, stating the research/engineering question
  that you want to get answered by your project.

>>>>

Visualization of knowledge is important to foster learning. To optimize the representation of knowledge and its interdependencies, we will focus on identifying ways to present knowledge without loosing context. This research aims at taking an existing annotated corpus and presenting its contents in a way that allows the audience to see the dependencies of the covered topics. This form of presenting the knowledge should make it easy to examine materials that form the basis for the topics the audience is interested in.\\

Consider the typical lecture one attends as a student. Towards the end of the lecture students might have difficulties remembering earlier topics. When introducing a new topic it would be ideal to have a simple way to find the knowledge dependencies and present students with a simple way to catch up.\\

If this research is successful one could envision connecting all of Mathematics or other fields in a way that allows students to go back to the concepts they have forgotten to understand the topics currently covered in class. As such it will foster learning and could transform how we interact with course material as a whole. It is easy to see that this research would also have many other real world applications anywhere where knowledge is supposed to be transferred.\\

@@

-addresses fellow experts from your field (but not from your particular topic of research). 
- Here you should technically connect to the main concepts from that field and give an outline of your project, stating the research/engineering question that you want to get answered by your project.
